### 2019-12-20 paper/educ_work_over_time.tex
Minor edits

Even as the level of female education has increased, the female labor force participation 
in both urban and rural areas has stagnated or decreased
\citep{Klasen2015,Afridi2018,Bhargava2018, Chatterjee2018, Bhargava2019}.
A decline in female labor force participation in the beginning of development is
consistent with the hypothesis of a U-shaped labor force participation as a country
develop, although India's female labor force participation is lower than most other
countries and more in line with countries in the Middle East and North Africa  
\citep{Goldin1994,Klasen2015,Chatterjee2018}.

>>>>

Even as the level of female education has increased, the female labor force participation 
in both urban and rural areas has stagnated or decreased
\citep{Klasen2015,Afridi2018,Bhargava2018, Chatterjee2018, Bhargava2019}.
A decline in female labor force participation in the beginning of development is
consistent with the hypothesis of a U-shaped labor force participation as a country
develop \citep{Goldin1994}
India's female labor force participation is, however,  lower than most other
countries and more in line with countries in the Middle East and North Africa and
does not yet show any signs of increasing.
\citep{Klasen2015,Chatterjee2018}.

India has experience substantial economic growth since the mid-seventies with
an average growth rate of about 5.5 percent from 1978 to 2004 \citet{Bosworth2008}.
